---
title: "assignment_b1"
author: "Mike Mask"
date: "`r Sys.Date()`"
output: 
    github_document:
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(testthat)
library(gapminder)
library(palmerpenguins)
library(ellipsis)
```

# Exercises 1 and 2: Function and Documentation

```{r}

#' Standardize and model numeric vectors
#' 
#' Standardizes two numeric vectors and automatically inputs the two vectors into a linear model 
#' 
#' @param criterion the variable to be predicted (note: I named this argument 'criterion' because it will be the criterion in the linear model that this function creates)
#' 
#' @param predictor the variable doing the predicting (note: I named this argument 'predictor' because it will be the predictor in the linear model that this function creates)
#' 
#' @return this function outputs the summary of a linear model consisting of standardized criterion and predictor variables



standardize_and_model <- function(criterion, predictor, remove_na = TRUE, ...) {
  #Ensures criterion is numeric
  ellipsis::check_dots_used()
  if(!is.numeric(criterion)) {
    stop("Sorry bud, your criterion is not numeric, it's a ", class(criterion))
  }
  #Ensures predictor is numeric
  if(!is.numeric(predictor)) {
    stop("Easy there, your predictor is not numeric, it's a ", class(predictor))
  }
  #Standardizes criterion and stores it as a
  a <- (criterion - mean(criterion, na.rm = remove_na, ...))/sd(criterion, na.rm = remove_na)
  #Standardizes predictor and stores it as b
  b <- (predictor - mean(predictor, na.rm = remove_na, ...))/sd(predictor, na.rm = remove_na)
  
  #Takes standardized variables and inputs into model object called c in which standardized criterion is being predicted by standardized predictor
  
  c <- lm(a ~ b)
  
  #Returns a summary of the model object
  
  return(summary(c))
}

```

# Exercise 3: Examples

**Example 1**:

The first example... DESCRIBE HERE and talk about output and comment code

```{r}
head(gapminder)

standardize_and_model(criterion = gapminder$lifeExp, predictor = gapminder$gdpPercap)
```

**Example 2**:

The second example... DESCRIBE HERE AND TALK ABOUT OUTPUT AND COMMENT CODE

```{r}
head(penguins)

standardize_and_model(criterion = penguins$body_mass_g, predictor = penguins$flipper_length_mm)

```

**Example 3**:

The third example... DESCRIBE HERE AND TALK ABOUT OUTPUT AND COMMENT CODE

```{r}
head(mtcars)

standardize_and_model(mtcars$mpg, mtcars$cyl)
```

**Example 4**:

The fourth example demonstrates that when the criterion argument is not numeric (in this case it's a factor - the country) the function outputs an informative error message telling us that the criterion is not numeric, it's a factor.

```{r, error=TRUE}
head(gapminder)

standardize_and_model(gapminder$country, gapminder$lifeExp)
```


**Example 5**:

The fifth example demonstrates that when the predictor argument is not numeric (in this case it's a factor - the country) the function outputs an informative error message telling us that the predictor is not numeric, it's a factor.

```{r, error=TRUE}
head(gapminder)

standardize_and_model(gapminder$lifeExp, gapminder$country)
```

# Exercise 4: Testing the Function

**Test 1**:

```{r}
test_that("TYPE HERE", {
expect_error(standardize_and_model(gapminder$lifeExp, gapminder$country), "Easy there, your predictor is not numeric, it's a factor")
})
```

**Test 2**:

```{r}
a <- (gapminder$lifeExp - mean(gapminder$lifeExp))/sd(gapminder$lifeExp)
b <- (gapminder$gdpPercap - mean(gapminder$gdpPercap))/sd(gapminder$gdpPercap)

test_that("TYPE HERE", {
  expect_equal(standardize_and_model(criterion = gapminder$lifeExp, predictor = gapminder$gdpPercap),
                   summary(lm(a ~ b)))
})
```

**Test 3**:
PUT THIS ONE FIRST!!!!!!!!!!!!!!!!!
```{r}
test_that("TYPE HERE", {
  expect_is(standardize_and_model(criterion = gapminder$lifeExp, predictor = gapminder$gdpPercap),
            "summary.lm")
})
```



TO-DO LIST:
README
COMMENT CODE
REVIEW

